%-------------------------
% Resume in Latex
% Author : Burak Özkan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://bozkan.me/}{\Large Burak Özkan}} & Email : \href{mailto:burakozkan.ceng@gmail.com}{sourabh@sourabhbajaj.com}\\
  \href{http://bozkan.me/}{bozkan.me} & Mobile : +90-535-574-8368 \\
\end{tabular*}
\href{https://github.com/BurakOzkan/}{github.com/BurakOzkan/}\\
\href{https://inkedin.com/in/ozkan-burak}{linkedin.com/in/ozkan-burak}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ege University}{IZMIR, Turkey}
      {Bachelor's Degree in Computer Engineering;  GPA: 3.12}{Sep. 2015 -- Sep. 2019}

    \resumeSubheading
      {Republic Anatolian Highschool}{ESKISEHIR, Turkey}
      {}{2008 - 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    
    \resumeSubheading
      {Jotform}{IZMIR, Turkey}
      {Software Engineer Intern}{Jul 2019 - Sep 2019}
      \resumeItemListStart
        \resumeItem{React}
          {React is an open-source front-end JavaScript library for building user interfaces or UI components. It is maintained by Facebook and a community of individual developers and companies.}
        \resumeItem{Jotform API}
          {JotForm API allows you to access your JotForm account, forms and form submissions. Writing applications, integrations and scripts with JotForm API is very easy since it is based on REST principles. Code samples are also available on most common languages such as PHP, Java, Python, NodeJS and GO.}
        \resumeItem{NodeJS}
          {Node.js is an open-source, cross-platform, back-end JavaScript runtime environment that runs on the V8 engine and executes JavaScript code outside a web browser.}

      \resumeItemListEnd
      
    \resumeSubheading
      {Vestel - Currently }{MANISA, Turkey}
      {Software Engineer}{Nov 2019 - Present}
      \resumeItemListStart
        \resumeItem{EVC R\&D}
          {Some of Vestel's Electric Vehicle Chargers contain human-machine interfaces.These human-machine interfaces are connected to central systems with the Open Charge point protocol.}
          \resumeItem{OCPP Protocol Security Specifications }
          {The Open Charge Point Protocol (OCPP) is an application protocol for communication between Electric vehicle (EV) charging stations and a central management system, also known as a charging station network, similar to cell phones and cell phone networks. Worked on Websocket, OpenSSL, C and Cross Compiling For Arm Based Systems. Dev.Technologies Used In: CMake, gdbserver, Subversion }
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------




  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Android Mobile Application Prototype for Advisee's}
      {  This project includes two types of users, client and consultant. Implementations were made at the prototype level. Implementations: user profiles and chat system.
Technologies used Android Studio, Java, Firebase  (Graduation Project)(2018-2019)}
    \resumeSubItem{Contest Program Simulation}
      {Algorithms Course - CLI (C) (2015)}
    \resumeSubItem{Airline Reservation System Database}
      {Database Course - Database Design Prototype with SQL Queries}
    \resumeSubItem{School Website Demo}
      {Web Programming Course - JavaScript, JQuery, CSS, HTML}
    \resumeSubItem{Side Projects} 
      {Website Scrapping with Python Beautiful Soup 4 Tech Stack: Telegram API, Python, AWS EC2  }
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C/C++, Python, Javascript, SQL, Typescript }
      \hfill
      \\
      \textbf{Technologies Used}{: AWS, GCP, React, NodeJS, GCE, CMake, Linux, VSCODE, Docker, AWS EC2, AWS Lightsail, Subversion/Git}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
